Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-08-25 ising/Fibonacci/about.tex

\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,
    foot=1cm,bottom=1.5cm]{geometry}

@@

The line $L = \{ x\in \mathR\ s.t.\ |x|\leq 1 \} $,
and a finite set $R_n\subset L$,
$L_n = (L, R_n).$

We define a curve diagram as an embedding $f : L\to D$ that
restricts to an injection $R_n\to Q_n,$ modulo
isotopy.
This will be denoted as $f : L_n\to D_n.$
We can generalize this to $f : L_m\to D_n$ with $m\leq n$
to mean a map $L\to D$ that restricts to an injection $R_m\to Q_n,$
modulo isotopy.

DIAGRAM

@@

\important{Definition:} by a {\it local action} on a curve
diagram $f:L_n\to D_n$ we mean an element of $MCG(D_n)$
that can be represented by a half-twist that acts
on a small neighbourhood of $f([i, i+1]).$
We denote such an element by $b(i, f).$

\important{Definition:} by a {\it sequence of local moves} on a curve
diagram $f:L_n\to D_n$ we mean a
sequence of curve diagrams $f_k: L_n\to D_n$ and local actions:

@@

\heading{Local factorization of $MCG(D_n)$}

\important{Problem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of local moves such that % DIAGRAM
$g = \phi f i.$

@@

>>>>

%\usepackage[paper=a4paper,dvips,top=1.5cm,left=1.5cm,right=1.5cm,foot=1cm,bottom=1.5cm]{geometry}
\usepackage[paper=a4paper,dvips,top=3.0cm,left=1.5cm,right=1.5cm,foot=1cm,bottom=1.5cm]{geometry}

@@

The line $L = \{ x\in \mathR\ s.t.\ |x|\leq 1 \} $,
and a finite set $R_n\subset L$,
$L_n = (L, R_n).$
By a slight abuse of notation, we enumerate the points in $R_n$ 
in a monotonically increasing order,
and understand such notation as $[i, i+1]$ to mean the closed interval in $L$
with (consecutive) endpoints $i, i+1 \in R_n.$

We define a curve diagram as an embedding $f : L\to D$ that
restricts to a bijection $R_n\to Q_n,$ modulo
isotopy.
This will be denoted as $f : L_n\to D_n.$
We can generalize this to $f : L_m\to D_n$ with $m\leq n$
to mean a map $L\to D$ that restricts to an injection $R_m\to Q_n,$
modulo isotopy.

\begin{center}
\includegraphics[width=0.5\textwidth]{curve-diagram.eps}
\end{center}

@@

\important{Definition:} by a {\it half-twist} on a curve
diagram $f:L_n\to D_n$ at $i$ we mean an element of $MCG(D_n)$
that can be represented by a half-twist that acts
on a small neighbourhood of $f([i, i+1]).$
We denote a clockwise half-twist by $b(i, f):$

\begin{center}
\includegraphics[width=0.2\textwidth]{halftwist-1.eps}
\includegraphics[width=0.15\textwidth]{halftwist-2.eps}
\end{center}

See \cite{Kassel10} for more details on half-twists.

\important{Definition:} by a {\it sequence of half-twists} on a curve
diagram $f:L_n\to D_n$ we mean a
sequence of curve diagrams $f_k: L_n\to D_n$, and a sequence of half-twists:

@@

\heading{Half-twist factorization of $MCG(D_n)$}

\important{Problem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of half-twists such that % DIAGRAM
$g = \phi f i,$ where $i$ is an inclusion of $L_2$ into $L_n:$

\begin{center}
\includegraphics{halftwist-factor.eps}
\end{center}

\important{Examples:}

In this example we use an inverse half-twist about the segment $[a, a+1]:$

\begin{center}
\includegraphics[width=0.6\textwidth]{example-problem-1.eps}
\end{center}

@@

\heading{Combinatorial Formulation}

\heading{Numerical Simulations}
